---
title: "How to use minifars package"
author: "Constantin Cosma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"How to use minifars package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(minifars)
```

## General Info

This package queries and plot information about fatal traffic accidents using FARS data.
FARS represents data from the __US National Highway Traffic Safety Administration's Fatality Analysis Reporting System__, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.
You can find detailed information at the location [FARS](https://crashstats.nhtsa.dot.gov/#/DocumentTypeList/4).

## The Data

The package comes with the files `accident_2013.csv.bz2`, `accident_2014.csv.bz2` and `accident_2015.csv.bz2`. If you want to use the data, use those steps:

1. the working directory becomes the directory with data
```{r, eval=FALSE}
library(minifars)
save_ <- getwd()
dir_data <- system.file("extdata", file="accident_2013.csv.bz2", package="minifars")
setwd(dirname(dir_data))
```

2. use the functions from package

3. return to the original directory
```{r, eval=FALSE}
getwd(save_)
```

__Note.__
It's sufficient to create a directory on your disk (named `datafars` for example) and copy there the file of data. Before you use the functions from package, set the working directory there.


## The functions

The users have access to two functions from package:

1. `fars_summarize_years`

`fars_summarize_years` - creates a summary of number of accidents (_from a vector of years_) grouped by month and year.

```{r, eval=FALSE}
fars_summarize_years(years=2014)
fars_summarize_years(c(2014, 2015))
```


2. `fars_map_state`

`fars_map_state` draws a map (of _state.num_) with the positions (longitude and latitude) of accidents from a _year_. Here _stat.num_ is a vector of length 1, representing the identification code for a state. (see [state_code](https://crashstats.nhtsa.dot.gov/Api/Public/ViewPublication/812315#27)).
Parameter _year_ is a vector of length 1, representing the year when accidents was happened.


```{r, eval=FALSE}
fars_map_state(state.num=24, year=2014)
fars_map_state(1, year=2015)
```
